An open source scientific article about extrasolar magma oceans

### 2022-08-02 src/tex/ms.tex
update flowchart
add figure showing which planets have magma oceans

\begin{figure*}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/flowchart}
        \caption{Workflow of our hypothesis testing with Bioverse. In the first block, a stellar sample is generated based on XXX. The stars are then populated with planetary systems from XXX, to which a population-level trend can be applied. The planets' respective transit probabilities are computed. The second block simulates the exoplanet survey whereby selection effects and detection biases are introduced. Finally, the third block deals with testing a hypothesis based on the data from the simulated survey. By iterating through these steps, we compute the statistical power of testing the hypothesis given the assumed survey design.}
        \label{fig:flowchart}
    \end{centering}
\end{figure*}

@@

\subsubsection{Parametrization}
\todo{specific parametrization, dependency on bulk planet/orbit params (doesn't have to be its own subsubsection)}

@@

\subsection{Synthetic planet populations with and without magma oceans}
\todo{describe the way we inject magma oceans into the synthetic planet population with Bioverse}

>>>>

\begin{figure*}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/flowchart}
        \caption{Workflow of our hypothesis testing with Bioverse. In the first block, a stellar sample is generated based on XXX. The stars are then populated with planets from XXX, which may be assigned a magma ocean based on the model described in Sect.~\ref{sec:mo_model}. The planets' respective transit probabilities are computed. The second block simulates the exoplanet survey whereby selection effects and detection biases are introduced. Finally, the third block deals with testing a hypothesis based on the data from the simulated survey. By iterating through these steps, we compute the statistical power of testing the hypothesis given the assumed survey design.}
        \label{fig:flowchart}
    \end{centering}
\end{figure*}

@@

\subsubsection{Parametrization}
\label{sec:mo_model}
\todo{specific parametrization, dependency on bulk planet/orbit params (doesn't have to be its own subsubsection)}

@@

\subsection{Synthetic planet populations with and without magma oceans}
\todo{describe the way we inject magma oceans into the synthetic planet population with Bioverse}
\begin{figure*}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/has_magmaocean}
        \caption{Synthetic planets with and without magmaoceans as a function of Solar-equivalent semi-major axis}
        \label{fig:has_magmaocean}
    \end{centering}
\end{figure*}
